---
title: "DSjobtracker: What are the qualifications and skills that a data scientist, statistician, or data analyst must possess?"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---
<style>
.tab-content{
position:relative;
top:50px;
}
</style>
```{r setup, include=FALSE}
library(flexdashboard)
library(wordcloud)
library(wordcloud2)
library(tm)
library(RColorBrewer)
library(stringr)
library(tidyverse)
library(plotly)
library(data.table)
library(countrycode)
library(quantmod)
library(formattable)
library(ggwordcloud)
library(dplyr)
library(ggplot2) 
library(readr)
library(readxl)
library(sp)
library(gganimate)
library(ggpubr)
DStidy_2022 <- read_csv("DStidy_2022.csv")
```

Overview
======================================================
Column
-----------------------------------------------------------------------

### *Job Title*
```{r}

jbs <- str_to_lower(DStidy_2022$Job_title)
jbs <- gsub("[[:punct:]]"," ",jbs)

docs1 <- Corpus(VectorSource(jbs))
docs1 <-docs1 %>% 
  tm_map(removePunctuation) %>%  
  tm_map(removeWords,c("and", "–"))

dtm1 <-  TermDocumentMatrix(docs1)
matrix1 <- as.matrix(dtm1)
words1 <- sort(rowSums(matrix1),
               decreasing = TRUE)

jbstitle <- data.frame(word1= names(words1),
                       freq1 =words1)

set.seed(500)

wordcloud(words = jbstitle$word1,
          freq = jbstitle$freq1,  
          min.freq = 2,
          max.words=35,
          random.order=FALSE,
          font=4,
          family= "serif",
          root.per=1.5,
          scale = c(5,1.5),
          colors = brewer.pal(8,"Dark2"))

```

### *Education Qualification* 
```{r}

edu <- str_to_lower(DStidy_2022$Educational_qualifications)
edu <- gsub("[[:punct:]]"," ",edu)

edu <- edu %>% str_replace_all(c(
  "bachelor's" ="bsc",
  "bachelors" = "bsc",
  "bachelor" = "bsc",
  " bachelor" = "bsc",
  "bsc's" ="bsc",
  "master" = "msc",
  "masters"="msc",
  "masterss"="msc",
  "mscs"="msc"))

docs2 <- Corpus(VectorSource(edu))

docs2 <- tm_map(docs2,
                removeWords,
                c("any","etc","with","higher","and","other",
                  "such","related","data","field","of"))

dtm2 <-  TermDocumentMatrix(docs2)
matrix2 <- as.matrix(dtm2)
words2 <- sort(rowSums(matrix2),
               decreasing = TRUE)

eduQua <- data.frame(word2= names(words2),
                     freq2 =words2)

set.seed(2017)

wordcloud(words = eduQua$word2,
          freq = eduQua$freq2,  
          min.freq = 2,
          max.words=45, 
          random.order=FALSE,
          font=4,
          family= "serif",
          root.per=1.5,
          scale = c(4,1),
          colors = brewer.pal(8,"Dark2"))

```


Column
-----------------------------------------------------------------------

### *Job Category* 
```{r}

knw <- DStidy_2022$Job_Category

docs3 <- Corpus(VectorSource(knw))
docs3 <- docs3 %>% 
  tm_map(removePunctuation)
docs3 <- tm_map(docs3,
                removeWords,
                c("with"," knowledge","and","from","for",
                  "the","large"," etl ","using","that",
                  "our","strong","including","methods"))

dtm3 <-  TermDocumentMatrix(docs3)
matrix3 <- as.matrix(dtm3)
words3 <- sort(rowSums(matrix3),
               decreasing = TRUE)

knwBase <- data.frame(word3=names(words3),
                      freq3=words3)

wordcloud(words = knwBase$word3,
          freq = knwBase$freq3, 
          min.freq = 2,
          max.words=35, 
          random.order=FALSE,
          font=4,
          family= "serif",
          root.per=1.5,
          scale = c(5,1.5),
          colors = brewer.pal(8,"Dark2"))

```

### *Company Location* 
```{r}

# Data Cleaning 
DStidy_2022$Country[DStidy_2022$Country == "110 Healthy Way, Folosm, CA"] <- "US"
DStidy_2022$Country[DStidy_2022$Country == "United Kingdom"] <- "UK"
DStidy_2022$Country[DStidy_2022$Country == "Sri Lnaka"] <- "Sri Lanka"
DStidy_2022$Country[DStidy_2022$Country == "SL"] <- "Sri Lanka"
DStidy_2022$Country[DStidy_2022$Country == "Bloomington, IN"  ] <- "US"
DStidy_2022$Country[DStidy_2022$Country == "Edinburgh,London,Manchester"] <- "UK"
DStidy_2022$Country[DStidy_2022$Country == "Nodia,Uttar Pradesh,India"] <- "India"
DStidy_2022$Country[DStidy_2022$Country == "Melbone" ] <-  "Australia"
DStidy_2022$Country[DStidy_2022$Country == "canada"] <- "Canada "
DStidy_2022$Country[DStidy_2022$Country == "Pennsylvania" ] <- "US"  
DStidy_2022$Country[DStidy_2022$Country == "united states"] <-  "US" 
DStidy_2022$Country[DStidy_2022$Country ==  "Sri lanka" ] <- "Sri Lanka"
DStidy_2022$Country[DStidy_2022$Country == "NewYork"] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "Sri lanka" ] <- "Sri Lanka"
DStidy_2022$Country[DStidy_2022$Country == "santa monica,CA" ] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "Anaheim, CA"] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "Bengaluru, Karnataka, India"] <- "India"
DStidy_2022$Country[DStidy_2022$Country == "United States"  ] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "Noida,Uttar Pradesh, India" ] <- "India"
DStidy_2022$Country[DStidy_2022$Country == "Remote Work" ] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "USA" ] <- "US"
DStidy_2022$Country[DStidy_2022$Country ==  "Canada " ] <- "Canada"

DStidy_2022$Country[DStidy_2022$Country %>% is.na()] <- "US"

coun <- str_to_upper(DStidy_2022$Country)
coun<- gsub(" ","_",coun)

docs4 <- Corpus(VectorSource(coun))
docs4 <- tm_map(docs4,stripWhitespace)
docs4 <- tm_map(docs4,content_transformer(str_to_title))
dtm4 <-  TermDocumentMatrix(docs4)

matrix4 <- as.matrix(dtm4)
words4 <- sort(rowSums(matrix4),
               decreasing = TRUE)

loc <- data.frame(word4 = names(words4),freq4 =words4)

set.seed(2017)

wordcloud(words = loc$word4,
          freq = loc$freq4, 
          min.freq = 2,
          max.words=16, 
          random.order=FALSE,
          font=4,
          family= "serif",
          root.per=1.5,
          scale = c(6,1.5),
          colors = brewer.pal(8,"Dark2"))

```


Spatial Distributions
======================================================

Row 
-------------------------------------

### Spatial Distribution of proportion of Job Advertisments
    

### Advertisment Distribution by country



Row {.tabset .tabset-fade}
-------------------------------------
   
### Spatial Distribution by Job Type

 
### Spatial Distribution of Salary

*The minimum annual salary of each country in USD
    



Job Fields
======================================================

Column
--------------------------------------------------------------

### Composition of Job Fields



Column {.tabset .tabset-fade}
--------------------------------------------------------------

### R and Python Requirements of Job Fields


### Tableau and Microsoft Power BI Requirements of Job Fields


### Minimum experience needed in Job Fields


English Requirement
======================================================

## Column {data-width=500}
--------------------------------------------------------------

### English Requirement by Country



## Column {data-width=500, .tabset}
--------------------------------------------------------------

### English Requirement by Job Field


### English Requirement by Job Category




Soft Skills
======================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Composition of demanded Soft Skills


Column {data-width=650}
-----------------------------------------------------------------------

### Demanded Soft Skills according to the Job Field





Experience
======================================================

```{r}
## Packages
library(tidyverse)
library(plotly)
library(DSjobtracker)
```


```{r}
## Install the data set
DStidy_2022 <- read_csv("DStidy_2022.csv")
DStidy_2022 <- DStidy_2022 %>% mutate(`Minimum Experience in Years` = case_when(
 `Minimum Experience in Years` %in% c(0.5,1) ~ 1,
 `Minimum Experience in Years`== 0 ~ 0 ,
  `Minimum Experience in Years`== 2 ~ 2,
  `Minimum Experience in Years`== 3 ~ 3,
  `Minimum Experience in Years`== 4 ~ 4,
  `Minimum Experience in Years`== 5 ~ 5,
  `Minimum Experience in Years`== 6 ~ 6,
  `Minimum Experience in Years`== 7 ~ 7,
  `Minimum Experience in Years`== 8 ~ 8,
  `Minimum Experience in Years`== 10 ~ 10,
  `Minimum Experience in Years`== 12 ~ 12
))
  

```

column{}
----------------------------------------------------------------------

### Distribution of Minimun Years of Experience

```{r}
plot_ly(DStidy_2022,
        x = ~`Minimum Experience in Years`,
        type = "histogram") %>%
  layout(xaxis = list(title = "Minimum Required Experience in Years"),
         yaxis = list(title = "No of Job Advertisements"), 
         showlegend = FALSE)
```


column{.tabset}
-----------------------------------------------------------------------

### Distribution of Experience by Job Category

```{r}
DStidy_2022 <- DStidy_2022 %>% mutate(`Job_Category` = case_when(
   `Job_Category` %in% c("Business Analytics","Business/Systems Analysts","Finance and Sales","Business Development and Sales","Administrative","Human Resources Services", "Consulting, Information Technology, and Sales","Information Services","IT Services") ~ "Buisness Analyst",
  
   `Job_Category` %in% c("Data Science","Database Systems","Statistics","Data science","Research, Consulting, and Analyst","Actuarial Science","Information Technology, Analyst,and Science","Machine Learning","AI", "Artificial Intelligence") ~ "Data Scientist",
 
    `Job_Category` %in% c("Data Analyst","Science & Technology","Sciences","Internet Publishing" ,"Science and Analyst","Analyst","Research, Consulting, and Analyst","Research, Analyst, and Information Technology") ~ "Data Analyst",
 
    `Job_Category` %in% c( "Engineering - Software","Engineering, Mechanical" ,"Data Engineering","Software Developmwnt","Information Technology", "Computer/Information Technology","IT","Analyst, Engineering and Information Technology","Management, Engineering and Analyst","Engineering and Information  Technology","Information Technology and Analyst")~"Data Engineering"
 

))
data_exp <- DStidy_2022 %>% filter(Job_Category != "NA")

plot_ly(data_exp,
        x = ~Job_Category,
        y = ~`Minimum Experience in Years`,
        type = "box",
        color = ~Job_Category,
        colors = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a","blue")) %>%
  layout(xaxis = list(title  = "Job Category", tickangle = 0),
         yaxis = list(title = "Minimum Required Experience in Years"), showlegend = FALSE)
```

### Distribution of Experience by Educational Qualifications


```{r}

edu <- DStidy_2022 %>% select("BSc_needed","MSc_needed","PhD_needed","Minimum Experience in Years")

# convert data set into numeric
edu1 <- as.data.frame(apply(edu, 2, as.numeric))

education <- replace(edu1, is.na(edu1), 1)


data_new <- pivot_longer(education, c(1:3), names_to = "Education", values_to = "Value")



data2 <- data_new %>% filter(Value == 1)


plot_ly(data2,
        x = ~ Education,
        y = ~`Minimum Experience in Years`,
        type = "box",
        color = ~Education,
        colors = c("#e41a1c", "#377eb8", "#4daf4a")) %>%
  layout(xaxis = list(title  = "Minimum Educational Qualifications", tickangle = 0),
         yaxis = list(title = "Minimum Required Experience in Years"), showlegend = FALSE)

```





Software and Skills
======================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Top 20 skills required in jobs

```{r}

Top_skills_required<- DStidy_2022%>%
  select(c(AI:Web_Analytic_tools)) %>%
  pivot_longer(c(AI:Web_Analytic_tools), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value, na.rm = TRUE)) %>% 
  arrange(Total) 
  
  Top_skills_required %>%
  mutate(Name = factor(Name, levels = .$Name)) %>%
  top_n(20) %>%
plot_ly(
        x= ~Total,
        y= ~reorder(Name,Total),
        type = "bar",
   marker = list(color = "hsl(0,100%,50%))") ,height = 600,width = 700)  %>% 
 
layout(title = "Top 20 Skills Required in Jobs",xaxis = list(title = "No of Job Advertisments"),
         yaxis =list(title = "Skills Required"))
```



Column {data-width=500}
-----------------------------------------------------------------------

### Soft skills required in jobs

```{r}

 Soft_skills_required<- DStidy_2022%>%
  select(c(Presentation_Skills:`agile execution`)) %>%
  pivot_longer(c(Presentation_Skills:`agile execution`), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value, na.rm = TRUE)) %>% 
  arrange(Total) 

Soft_skills_required %>%
  plot_ly(labels = ~Name,
          values = ~Total,
          parents = NA,
          type = "treemap", height = 600, width = 650, textinfo = "label+value+percent parent") %>%
  layout(title = "Soft Skills Required in Jobs")

```


Software Skills
======================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Statistical softwares

```{r}

Statistical_software <- paste(DStidy_2022$R,DStidy_2022$SAS,DStidy_2022$SPSS,DStidy_2022$Python,sep = "::")


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]

Statistical_software[Statistical_software=="1::0::0::0"] <-"R only"
Statistical_software[Statistical_software=="0::0::0::1"] <-"Python only"
Statistical_software[Statistical_software=="0::1::0::0"] <-"SAS only"
Statistical_software[Statistical_software=="1::0::0::1"] <-"R & Python"
Statistical_software[Statistical_software=="1::1::0::1"] <-"R, SAS & Python only "
Statistical_software[Statistical_software=="0::0::0::0"] <-"No statistical softwares"
Statistical_software[Statistical_software=="0::1::0::1"|
                     Statistical_software=="1::1::1::1"|
                     Statistical_software=="0::1::1::1"|
                     Statistical_software=="1::1::1::0"|
                     Statistical_software=="0::0::1::0"|
                     Statistical_software=="1::0::1::0"|
                     Statistical_software=="1::0::1::1"|
                     Statistical_software=="0::1::1::0"|
                     Statistical_software=="0::1::0::NA"|
                     Statistical_software=="0::0::1::1"|
                     Statistical_software=="1::1::0::0"] <- "Other statistical softwares"


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]


d1 %>% plot_ly(x = ~Frequency, y = ~reorder(Statistical_software, Frequency), 
               type =  'bar', orientation = 'h') %>% 
  layout(title = "", 
         xaxis = list(title = "Number of job advertisements" ,zeroline = FALSE),
         yaxis = list(title = "", zeroline = FALSE))

```



Column {data-width=500}
-----------------------------------------------------------------------

### Database and Query languages

```{r}
Database_and_Query_languages <- paste(DStidy_2022$SQL,DStidy_2022$NoSQL,DStidy_2022$MySQL,DStidy_2022$Hadoop,sep = "::")


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


Database_and_Query_languages[Database_and_Query_languages=="1::0::0::0"] <-"SQL only"
Database_and_Query_languages[Database_and_Query_languages=="1::0::1::0"] <-"SQL & MySQL"
Database_and_Query_languages[Database_and_Query_languages=="1::0::0::1"] <-"SQL & Hadoop"
Database_and_Query_languages[Database_and_Query_languages=="1::1::0::0"] <-"SQL & NoSQL"
Database_and_Query_languages[Database_and_Query_languages=="0::0::0::0"] <-"No database or query languages"

Database_and_Query_languages[Database_and_Query_languages=="0::0::1::0"|
                             Database_and_Query_languages=="0::1::0::0"| 
                             Database_and_Query_languages=="0::0::0::1"| 
                             Database_and_Query_languages=="1::1::1::1"| 
                             Database_and_Query_languages=="1::1::0::1"| 
                             Database_and_Query_languages=="1::0::1::1"| 
                             Database_and_Query_languages=="0::1::1::1"| 
                             Database_and_Query_languages=="0::0::NA::0"| 
                             Database_and_Query_languages=="1::1::1::0"] <- "Other"


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


d2 %>% plot_ly(x = ~Frequency, y = ~reorder(Database_and_Query_languages, Frequency), 
               type =  'bar', orientation = 'h', color = "red") %>% 
  layout(title = "", 
         xaxis = list(title = "Number of job advertisment" ,zeroline = FALSE), 
         yaxis = list(title = ""))


```



Knowledge and Skills
======================================================

```{r, message=FALSE, include=FALSE}

## changing column names 
colnames(DStidy_2022)[colnames(DStidy_2022) == "Natural_Language_Processing(NLP)"] = "Natural Language Processing"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_Pipelines"] = "Data Pipelines"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Machine_Learning"] = "Machine Learning"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Computer_vision"] = "Computer Vision"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_visualization"] = "Data Visualization"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_warehouse"] = "Data Warehouse"
colnames(DStidy_2022)[colnames(DStidy_2022) == "BigData"] = "Big Data"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_management"] = "Data Management"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_mining"] = "Data Mining"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_science"] = "Data Science"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Numerical_Analysis"] = "Numerical Analysis"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Problem_Solving"] = "Problem Solving"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Team_Handling"] = "Team Handling"
colnames(DStidy_2022)[colnames(DStidy_2022) == "agile execution"] = "Agile Execution"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Data_marketing"] = "Data Marketing"
colnames(DStidy_2022)[colnames(DStidy_2022) == "SEO"] = "Search Engine Optimization"
colnames(DStidy_2022)[colnames(DStidy_2022) == "graphics_and_design_skills"] = "Graphic Designing"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Content_Management"] = "Content Management"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Economic"] = "Economic Knowledge"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Finance_Knowledge"] = "Finance Knowledge"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Investment_Knowledge"] = "Investment Knowledge"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Debtor_reconcilation"] = "Debtor Reconcilation"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Presentation_Skills"] = "Presentation Skills"
colnames(DStidy_2022)[colnames(DStidy_2022) == "Payroll_management"] = "Payroll Management"
colnames(DStidy_2022)[colnames(DStidy_2022) == "AI"] = "Artificial Intelligence"
colnames(DStidy_2022)[colnames(DStidy_2022) == "IOT"] = "IOT (Internet of Things)"
```

Column {data-width=650}
-----------------------------------------------------------------------

### Treemap of Knowledge and skills

```{r, message=FALSE, warning=FALSE}
## tree map 

ks<-DStidy_2022 %>% select(c(`Artificial Intelligence`:`IOT (Internet of Things)`,`Presentation Skills`:`Payroll Management`))

df<-ks%>%pivot_longer(1:30)
colnames(df)[1] <- "Knowledge and Skills"
colnames(df)[2] <- "Cases"
df<- df %>%group_by(`Knowledge and Skills`) %>%
  summarize(No_of_Job_vacancies = sum(Cases))%>%mutate(parents="Knowledge and Skills") 

##plot
tree_all <- df%>%plot_ly(type="treemap",labels=~`Knowledge and Skills`,parents=~parents,values=~No_of_Job_vacancies,domain=list(column=0),
             textinfo="label+value+percent parent")
tree_all
```

## Column {.tabset}

### Knowledge

```{r,message=FALSE,warning = FALSE}
## preparing data
Job_Titles <- str_to_lower(DStidy_2022$Job_title)
Job_Titles <- str_trim(Job_Titles)

DS <- Job_Titles[str_detect(Job_Titles, "([data]{4}|machine)[&a-z\\s]*([scientist]{7,10})|\\s+ai")] %>% unique() 
DE <- Job_Titles[str_detect(Job_Titles, "([data]{4}|machine|intelligence)[&a-z\\s]*([engineer]{8,9})")] %>% unique()
DA <- Job_Titles[str_detect(Job_Titles, "anal|statist|actuarial|research|statician")] %>% unique()

DA <- DA %>% append(Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique() %>% .[str_detect(.,"data\\s+")]) 
DS <- DS %>% append(Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique() %>% .[str_detect(.,"machine\\s+")])

DA <- DA[!DA%in%DS]
DA <- DA[!DA%in%DE]
DS<-DS[!DS%>%is.na()]
DE<-DE[!DE%>%is.na()]
Unimportant <- Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique()

DStidy_2022  <- DStidy_2022 %>% mutate(Job_Titles, Job_Category= 
                                         ifelse(Job_Titles%in%DS & Job_Titles%in%DE, "Data Science and Data Engineering", 
                                                ifelse(Job_Titles%in%DS, "Data Science", ifelse(Job_Titles%in%DA,"Data Analyst", "Other" ) ) )) 

## dot chart 
df1<-DStidy_2022%>%select(c(`Artificial Intelligence`:`IOT (Internet of Things)`,Job_Category))
                          
df11 <- df1 %>% pivot_longer(1:16) 

colnames(df11)[2] <- "Knowledge"
colnames(df11)[3] <- "Cases"

df12 <- df11 %>% filter(Cases == 1) 
df12 <- df12 %>% group_by(Knowledge,Job_Category) %>% count()

p2<- ggdotchart(df12,x = "Knowledge" ,y="n",color = "Job_Category",palette = c("#00AFBB","#E7B800","#FC4E07","#FF1493","#7FFFD4"),sorting = "asc",sort.by.groups=TRUE,add="segments",add.params = list(color="lightgray",size=2),dot.size = 4,ggtheme =theme_pubclean())+ font("x.text",size=8,vjust=0.5)+labs(x="Required Knowledge ",y="Count")

ggpar(p2,legend.title = "")%>%ggplotly()%>%layout(legend=list(orientation="h",xanchor="center",x=0.5,y=1.6))
```

### Other required skills 
```{r,message=FALSE,warning = FALSE}
## preparing data 

df2<-DStidy_2022%>%select(c(`Presentation Skills`:`Payroll Management`,Job_Category))
df21 <- df2 %>% pivot_longer(1:14) 
## changing column name 
colnames(df21)[2] <- "Skills"
colnames(df21)[3] <- "Cases"

df22 <- df21 %>% filter(Cases == 1) 
df22 <- df22 %>% group_by(Skills,Job_Category) %>% count()

## dot chart 
p3<- ggdotchart(df22,x = "Skills" ,y="n",color = "Job_Category",palette = c("#00AFBB","#E7B800","#FC4E07","#FF1493","#7FFFD4"),sorting = "asc",sort.by.groups=TRUE,add="segments",add.params = list(color="lightgray",size=2),dot.size = 4,ggtheme =theme_pubclean())+ font("x.text",size=8,vjust=0.5)+labs(x="Required Skills ",y="Count")

ggpar(p3,legend.title = "")%>%ggplotly()%>%layout(legend=list(orientation="h",xanchor="center",x=0.5,y=1.6))
```

Education
======================================================

```{r , include=FALSE}
library(flexdashboard)
library(plotly)
library(dplyr)
```

```{r data}
edu <- DStidy_2022 %>% select("BSc_needed","MSc_needed","PhD_needed")
# convert data set into numeric
edu1 <- as.data.frame(apply(edu, 2, as.numeric))
education <- replace(edu1, is.na(edu1), 1)
d <- education %>%
  rowwise() %>%
  mutate(degree = sum(BSc_needed,MSc_needed,PhD_needed, na.rm = T))

# Education qualification is classified based on the minimum level of education.
for(i in 1:nrow(d)){
 if((d[i,1] == 1 & d[i,4]>=1) == TRUE){  # BSc
    d$V3[i] <- "Bachelor's"
  }else if((d[i,1]== 0 & d[i,2] == 1 & d[i,4]>=1) == TRUE){  # MSc
    d$V3[i] <- "Master's"
  }else if ((d[i,3] == 1 & d[i,4]==1) == TRUE){ # PhD
    d$V3[i] <- "PhD"   
  }else if (( d[i,4]==0 ) == TRUE){  
    d$V3[i] <- "Other"
 
  }}  # other - There is no mention of a degree level, so there could be a different educational qualification. qualification 

d <- d %>% rename(degree_level = V3)
d <- d %>% select(-`degree`)
Final_edu <- d %>% group_by(degree_level) %>% 
  summarise(total_count=n(),
            .groups = 'drop')
Final_edu$degree_level <- factor(Final_edu$degree_level, levels = c("Other","PhD","Master's","Bachelor's"))
``` 


Column {data-width=200, .tabset}
-----------------------------------------------------------------------

### Educational Qualifications

```{r}
plot1 <- Final_edu %>% plot_ly(x = ~total_count, y = ~degree_level, type = 'bar',color = Final_edu$degree_level, domain = list(x = c(0, 0.5), y = c(0, 1))) %>% 
  layout(yaxis = list(title = " Minimum Education Qualification"),title= "Education Qualification",
    xaxis = list(title = "Number of Job Vacancies",tickangle=-45))
                               
  # layout(
  #   title= "Education Qualification",
  #   xaxis = list(title = "Number of Job Vacancies",tickangle=-45 ,c("Other","Diploma","Bachelor's","Master's","PhD")) ,
  #   yaxis = list(title = " Minimum Education Qualification"),font = list(color = 'black'))
plot1
```




Salary 
=====================================

Row
-------------------------------------

### Distibution of Average of Minimum Salaries by Job 


Row
------------------------------------
### Distibution of Average of Minimum Salaries by Countries


Inspiration
======================================================

Our Team
======================================================


