---
title: "DSjobtracker: What are the qualifications and skills that a data scientist, statistician, or data analyst must possess?"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---
<style>
.tab-content{
position:relative;
top:50px;
}
</style>
```{r setup, include=FALSE}
library(flexdashboard)
library(wordcloud)
library(wordcloud2)
library(tm)
library(RColorBrewer)
library(stringr)
library(tidyverse)
library(plotly)
library(data.table)
library(countrycode)
library(quantmod)
library(formattable)
library(ggplot2)
library(ggwordcloud)

DStidy_2022 <- read_csv("DStidy_2022.csv")
```

Overview
======================================================
Column
-----------------------------------------------------------------------

### Job Title

```{r}

set.seed(1)

##### ----- Job Title data ----- #####

# cleaning

overview_jobtitle <- DStidy_2022 %>% select(Job_title)

overview_jobtitle <- as.vector(overview_jobtitle)

overview_jobtitle_doc <- Corpus(VectorSource(overview_jobtitle))
overview_jobtitle_doc <- overview_jobtitle_doc %>% 
  tm_map(removeNumbers) %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stripWhitespace)
overview_jobtitle_doc <- tm_map(overview_jobtitle_doc, 
                                content_transformer(tolower))
overview_jobtitle_doc <- tm_map(overview_jobtitle_doc, 
                                removeWords, 
                                stopwords("english"))

overview_jobtitle_dtm <- TermDocumentMatrix(overview_jobtitle_doc)

overview_jobtitle_matrix <- as.matrix(overview_jobtitle_dtm)

overview_jobtitle_words <- sort(rowSums(overview_jobtitle_matrix), decreasing=TRUE)

overview_jobtitle_df <- data.frame(words=names(overview_jobtitle_words),
                                   freq=overview_jobtitle_words)

overview_jobtitle_df$words[overview_jobtitle_df$words=="adance"] <- "advance"
overview_jobtitle_df$words[overview_jobtitle_df$words=="birpython"] <- "biopython"
overview_jobtitle_df$words[overview_jobtitle_df$words=="dara"] <- "data"
overview_jobtitle_df$words[overview_jobtitle_df$words=="experiencehia"] <- "experience"
overview_jobtitle_df$words[overview_jobtitle_df$words=="dara"] <- "data"
overview_jobtitle_df$words[overview_jobtitle_df$words=="experiencehia"] <- "experience"
overview_jobtitle_df$words[overview_jobtitle_df$words=="intellegent"] <- "intelligent"
overview_jobtitle_df$words[overview_jobtitle_df$words=="per"] <- "permanenet"
overview_jobtitle_df$words[overview_jobtitle_df$words=="scienctist"] <- "scientist"
overview_jobtitle_df$words[overview_jobtitle_df$words=="scientists"] <- "scientist"

overview_jobtitle_df <- overview_jobtitle_df[!(row.names(overview_jobtitle_df) 
                                             %in% c("-", "csenior", "early", 
                                                    "fair", "sassqltableaupower")), ]

# visualization

ggplot(overview_jobtitle_df, aes(label=words, 
                                 size=freq, 
                                 color=factor(sample.int(10, 
                                                         nrow(overview_jobtitle_df), 
                                              replace = TRUE)))) + 
  ggtitle("") +
  geom_text_wordcloud_area() + 
  scale_size_area(max_size = 45) + 
  theme_bw() + 
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```

### Job Field

```{r}

set.seed(1)

##### ----- Job Field data ----- #####

# cleaning

overview_jobfield <- DStidy_2022 %>% select(Job_Field)

overview_jobfield <- as.vector(overview_jobfield)

overview_jobfield_doc <- Corpus(VectorSource(overview_jobfield))
overview_jobfield_doc <- overview_jobfield_doc %>% 
  tm_map(removeNumbers) %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stripWhitespace)
overview_jobfield_doc <- tm_map(overview_jobfield_doc, 
                                content_transformer(tolower))
overview_jobfield_doc <- tm_map(overview_jobfield_doc, 
                                removeWords, 
                                stopwords("english"))

overview_jobfield_dtm <- TermDocumentMatrix(overview_jobfield_doc)

overview_jobfield_matrix <- as.matrix(overview_jobfield_dtm)

overview_jobfield_words <- sort(rowSums(overview_jobfield_matrix), decreasing=TRUE)

overview_jobfield_df <- data.frame(words=names(overview_jobfield_words),
                                   freq=overview_jobfield_words)

overview_jobfield_df$words[overview_jobfield_df$words=="developmwnt"] <- "development"
overview_jobfield_df$words[overview_jobfield_df$words=="cdata"] <- "data"
overview_jobfield_df$words[overview_jobfield_df$words=="eqipment"] <- "equipment"

# visualization

ggplot(overview_jobfield_df, aes(label=words, 
                                 size=freq, 
                                 color=factor(sample.int(10, 
                                                         nrow(overview_jobfield_df), 
                                                         replace = TRUE)))) + 
  ggtitle("") +
  geom_text_wordcloud_area() + 
  scale_size_area(max_size = 30) + 
  theme_bw() + 
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```


Column
-----------------------------------------------------------------------

### Education Qualification

```{r}

set.seed(1)

##### ----- Education Qualifications ----- #####

# cleaning

eduquali_data <- DStidy_2022 %>% 
  select(Educational_qualifications)

eduquali_data <- as.vector(eduquali_data)

eduquali_data_doc <- Corpus(VectorSource(eduquali_data))

eduquali_data_doc <- eduquali_data_doc %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)

eduquali_data_doc <- tm_map(eduquali_data_doc, 
                            content_transformer(tolower))

eduquali_data_doc <- tm_map(eduquali_data_doc, 
                            removeWords, 
                            stopwords("english"))

eduquali_data_dtm <- TermDocumentMatrix(eduquali_data_doc)

eduquali_data_matrix <- as.matrix(eduquali_data_dtm)

eduquali_data_words <- sort(rowSums(eduquali_data_matrix), decreasing=TRUE)

eduquali_data_df <- data.frame(words = names(eduquali_data_words),
                               freq = eduquali_data_words)

# selecting the words that show frequency greater than or equal 5
eduquali_data_df_selected <- eduquali_data_df %>%
  filter(freq >= 5)

# correcting the spelling and dropping irrelevant words
eduquali_data_df_selected$words[eduquali_data_df_selected$words=="nanana"] <- NA
eduquali_data_df_selected$words[eduquali_data_df_selected$words=="field"] <- NA
eduquali_data_df_selected$words[eduquali_data_df_selected$words=="related"] <- NA

# omitting the rows with NA
eduquali_data_df_used <- na.omit(eduquali_data_df_selected)

# visualization

ggplot(eduquali_data_df_used, aes(label=words, 
                                  size=freq, 
                                  color=factor(sample.int(10, 
                                                         nrow(eduquali_data_df_used), 
                                                         replace = TRUE)))) + 
  ggtitle("") +
  geom_text_wordcloud_area() + 
  scale_size_area(max_size = 30) + 
  theme_bw() + 
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```

### Company Location

```{r}

set.seed(1)

##### ----- Country data ----- #####

# cleaning

overview_country <- DStidy_2022 %>% select(Country)

overview_country <- as.vector(overview_country)

overview_country_doc <- Corpus(VectorSource(overview_country))
overview_country_doc <- overview_country_doc %>% 
  tm_map(removeNumbers) %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stripWhitespace)
overview_country_doc <- tm_map(overview_country_doc, 
                               content_transformer(tolower))
overview_country_doc <- tm_map(overview_country_doc, 
                               removeWords, 
                               stopwords("english"))

overview_country_dtm <- TermDocumentMatrix(overview_country_doc)

overview_country_matrix <- as.matrix(overview_country_dtm)

overview_country_words <- sort(rowSums(overview_country_matrix), decreasing=TRUE)

overview_country_df <- data.frame(words=names(overview_country_words),
                                  freq=overview_country_words)

overview_country_df$words[overview_country_df$words=="lanka"] <- "srilanka"
overview_country_df$words[overview_country_df$words=="states"] <- "unitedstates"
overview_country_df$words[overview_country_df$words=="kingdom"] <- "unitedkingdom"
overview_country_df$words[overview_country_df$words=="arab"] <- "unitedarabemirates"
overview_country_df$words[overview_country_df$words=="arab"] <- "unitedarabemirates"
overview_country_df$words[overview_country_df$words=="new"] <- "newzealand"

overview_country_df <- overview_country_df[!(row.names(overview_country_df) 
                                             %in% c("united", "sri", "emirates", 
                                                    "csri", "czech")), ]

# visualization

ggplot(overview_country_df, aes(label=words, 
                                size=freq, 
                                color=factor(sample.int(10, 
                                                          nrow(overview_country_df), 
                                                          replace = TRUE)))) + 
  ggtitle("") +
  geom_text_wordcloud_area() + 
  scale_size_area(max_size = 20) + 
  theme_bw() + 
  theme(axis.line = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

```


Spatial Distributions
======================================================

Row 
-------------------------------------

### Spatial Distribution of proportion of Job Advertisments
    

### Advertisment Distribution by country



Row {.tabset .tabset-fade}
-------------------------------------
   
### Spatial Distribution by Job Type

 
### Spatial Distribution of Salary

*The minimum annual salary of each country in USD
    



Job Fields
======================================================

Column
--------------------------------------------------------------

### Composition of Job Fields



Column {.tabset .tabset-fade}
--------------------------------------------------------------

### R and Python Requirements of Job Fields


### Tableau and Microsoft Power BI Requirements of Job Fields


### Minimum experience needed in Job Fields


English Requirement
======================================================

## Column {data-width=500}
--------------------------------------------------------------

### English Requirement by Country



## Column {data-width=500, .tabset}
--------------------------------------------------------------

### English Requirement by Job Field


### English Requirement by Job Category




Soft Skills
======================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Composition of demanded Soft Skills


Column {data-width=650}
-----------------------------------------------------------------------

### Demanded Soft Skills according to the Job Field





Experience
======================================================

column{}
----------------------------------------------------------------------

### Distribution of Minimun Years of Experience


column{.tabset}
-----------------------------------------------------------------------

### Distribution of Experience by Job Category


### Distribution of Experience by Educational Qualifications






Software and Skills
======================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Top 20 skills required in jobs

```{r}

Top_skills_required<- DStidy_2022%>%
  select(c(AI:Web_Analytic_tools)) %>%
  pivot_longer(c(AI:Web_Analytic_tools), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value, na.rm = TRUE)) %>% 
  arrange(Total) 
  
  Top_skills_required %>%
  mutate(Name = factor(Name, levels = .$Name)) %>%
  top_n(20) %>%
plot_ly(
        x= ~Total,
        y= ~reorder(Name,Total),
        type = "bar",
   marker = list(color = "hsl(0,100%,50%))") ,height = 600,width = 700)  %>% 
 
layout(title = "Top 20 Skills Required in Jobs",xaxis = list(title = "No of Job Advertisments"),
         yaxis =list(title = "Skills Required"))
```



Column {data-width=500}
-----------------------------------------------------------------------

### Soft skills required in jobs

```{r}

 Soft_skills_required<- DStidy_2022%>%
  select(c(Presentation_Skills:`agile execution`)) %>%
  pivot_longer(c(Presentation_Skills:`agile execution`), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value, na.rm = TRUE)) %>% 
  arrange(Total) 

Soft_skills_required %>%
  plot_ly(labels = ~Name,
          values = ~Total,
          parents = NA,
          type = "treemap", height = 600, width = 650) %>%
  layout(title = "Soft Skills Required in Jobs")

```


Software Skills
======================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Statistical softwares

```{r}

Statistical_software <- paste(DStidy_2022$R,DStidy_2022$SAS,DStidy_2022$SPSS,DStidy_2022$Python,sep = "::")


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]

Statistical_software[Statistical_software=="1::0::0::0"] <-"R only"
Statistical_software[Statistical_software=="0::0::0::1"] <-"Python only"
Statistical_software[Statistical_software=="0::1::0::0"] <-"SAS only"
Statistical_software[Statistical_software=="1::0::0::1"] <-"R & Python"
Statistical_software[Statistical_software=="1::1::0::1"] <-"R, SAS & Python only "
Statistical_software[Statistical_software=="0::0::0::0"] <-"No statistical softwares"
Statistical_software[Statistical_software=="0::1::0::1"|
                     Statistical_software=="1::1::1::1"|
                     Statistical_software=="0::1::1::1"|
                     Statistical_software=="1::1::1::0"|
                     Statistical_software=="0::0::1::0"|
                     Statistical_software=="1::0::1::0"|
                     Statistical_software=="1::0::1::1"|
                     Statistical_software=="0::1::1::0"|
                     Statistical_software=="0::1::0::NA"|
                     Statistical_software=="0::0::1::1"|
                     Statistical_software=="1::1::0::0"] <- "Other statistical softwares"


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]


d1 %>% plot_ly(x = ~Frequency, y = ~reorder(Statistical_software, Frequency), 
               type =  'bar', orientation = 'h') %>% 
  layout(title = "", 
         xaxis = list(title = "Number of job advertisements" ,zeroline = FALSE),
         yaxis = list(title = "", zeroline = FALSE))

```



Column {data-width=500}
-----------------------------------------------------------------------

### Database and Query languages

```{r}
Database_and_Query_languages <- paste(DStidy_2022$SQL,DStidy_2022$NoSQL,DStidy_2022$MySQL,DStidy_2022$Hadoop,sep = "::")


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


Database_and_Query_languages[Database_and_Query_languages=="1::0::0::0"] <-"SQL only"
Database_and_Query_languages[Database_and_Query_languages=="1::0::1::0"] <-"SQL & MySQL"
Database_and_Query_languages[Database_and_Query_languages=="1::0::0::1"] <-"SQL & Hadoop"
Database_and_Query_languages[Database_and_Query_languages=="1::1::0::0"] <-"SQL & NoSQL"
Database_and_Query_languages[Database_and_Query_languages=="0::0::0::0"] <-"No database or query languages"

Database_and_Query_languages[Database_and_Query_languages=="0::0::1::0"|
                             Database_and_Query_languages=="0::1::0::0"| 
                             Database_and_Query_languages=="0::0::0::1"| 
                             Database_and_Query_languages=="1::1::1::1"| 
                             Database_and_Query_languages=="1::1::0::1"| 
                             Database_and_Query_languages=="1::0::1::1"| 
                             Database_and_Query_languages=="0::1::1::1"| 
                             Database_and_Query_languages=="0::0::NA::0"| 
                             Database_and_Query_languages=="1::1::1::0"] <- "Other"


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


d2 %>% plot_ly(x = ~Frequency, y = ~reorder(Database_and_Query_languages, Frequency), 
               type =  'bar', orientation = 'h', color = "red") %>% 
  layout(title = "", 
         xaxis = list(title = "Number of job advertisment" ,zeroline = FALSE), 
         yaxis = list(title = ""))


```



Knowledge and Skills
======================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Treemap of Konwledge and skills



Column {data-width=350}{.tabset .tabset-fade}
-----------------------------------------------------------------------

### Required Knowledge according to job category


### Required Skills according to job category





Education
======================================================

Column {data-width=200, .tabset}
-----------------------------------------------------------------------

### Educational Qualifications






Salary 
=====================================

Row
-------------------------------------

### Distibution of Average of Minimum Salaries by Job 


Row
------------------------------------
### Distibution of Average of Minimum Salaries by Countries


Inspiration
======================================================

Our Team
======================================================


